Storm surges in the Strait of Georgia simulated with a regional model

### 2015-01-04 AO_guides/manuscriptAO.tex
Changed rivers to green dots for better visibility

\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{Figures/bathy.pdf}
\caption{Model domain (highlighted area) including bathymetry, rivers (blue circles), and storm surge locations of interest  (red stars).}\label{fig:domain}
\end{figure}

@@

River input provides a significant volume of fresh water to the Salish Sea and can influence stratification, circulation, and primary productivity. However, most rivers in the domain are not gauged so parametrizations were required to represent river flow. \citet{morrison2011rivers} provides a method for estimating freshwater runoff in the Salish Sea region based on precipitation. Monthly runoff volumes for each watershed for each year from 1970 to 2012 were acquired from \citet{morrison2011rivers}, as well as monthly averages. Freshwater runoff from each watershed was divided among the rivers in that watershed. The area drained by each river was estimated from Toporama maps by the Atlas of Canada and watershed maps available on the Washington State government website. The watersheds included in our model were Fraser (which represents approximately 44\% of the freshwater input into our domain), Skagit (12\%), East Vancouver Island (North and South) (12\%), Howe (7\%), Bute (7\%), Puget (6\%), Juan de Fuca (5\%), Jervis (4\%) and Toba (3\%). The monthly flow from each river was input as a point source from 0 to 3 metres at the model point closest to the mouth of each river. Incoming water was assumed to be fresh and at surface temperature. A total of 150 rivers were parametrized by this method and their locations are indicated by the blue dots in Figure \ref{fig:domain}.

>>>>

\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{Figures/bathy.pdf}
\caption{Model domain (highlighted area) including bathymetry, rivers (green circles), and storm surge locations of interest  (red stars).}\label{fig:domain}
\end{figure}

@@

River input provides a significant volume of fresh water to the Salish Sea and can influence stratification, circulation, and primary productivity. However, most rivers in the domain are not gauged so parametrizations were required to represent river flow. \citet{morrison2011rivers} provides a method for estimating freshwater runoff in the Salish Sea region based on precipitation. Monthly runoff volumes for each watershed for each year from 1970 to 2012 were acquired from \citet{morrison2011rivers}, as well as monthly averages. Freshwater runoff from each watershed was divided among the rivers in that watershed. The area drained by each river was estimated from Toporama maps by the Atlas of Canada and watershed maps available on the Washington State government website. The watersheds included in our model were Fraser (which represents approximately 44\% of the freshwater input into our domain), Skagit (12\%), East Vancouver Island (North and South) (12\%), Howe (7\%), Bute (7\%), Puget (6\%), Juan de Fuca (5\%), Jervis (4\%) and Toba (3\%). The monthly flow from each river was input as a point source from 0 to 3 metres at the model point closest to the mouth of each river. Incoming water was assumed to be fresh and at surface temperature. A total of 150 rivers were parametrized by this method and their locations are indicated by the green dots in Figure \ref{fig:domain}.
